%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Events}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvhonors}

%---------------------------------------------------------
\cvhonor
  {Perspectives on cancer prevention} % Event
  [Talk: EMBER creates a unified space for independent breast cancer transcriptomic datasets enabling precision oncology] % Talk
  {Lausanne, Switzerland} % Location
  {Feb. 2024} % Date



%---------------------------------------------------------
\cvhonor
  {International workshop on cancer prevention} % Event
  [Transcriptomic based molecular landscape provides a framework for precision medicine in breast cancer] % Talk
  {Ghent, Belgium} % Location
  {Jun. 2023} % Date

%---------------------------------------------------------

\cvhonor 
  {Science and policy summer schoool} % Event
  [Organized by EPFL and ETH PhD students] % Title
  {Beatenberg, Switzerland} % Local
  {Jul. 2023} % Date

%---------------------------------------------------------

\cvhonor 
  {World Cancer Day} % Event
  [Could algorithms and computers help us with cancer prevention?] % Title
  {Lausanne, Switzerland} % Local
  {Feb. 2023} % Date

%---------------------------------------------------------
\cvhonor 
  {Talks at AstraZeneca} % Event
  [Understanding hormone signaling and its risks on estrogen receptor-positive breast cancer] % Title
  {Cambridge, UK} % Local
  {Nov. 2022} % Date

%---------------------------------------------------------
\cvhonor
  {II Congreso Internacional de Topología y Afines} % Event
  [TDA in action: using two-tier mapper to understand breast cancer] % Talk
  {Lima, Peru} % Location
  {Oct. 2022} % Date


%---------------------------------------------------------
\cvhonor
  {43rd Annual Conference of the International Society for Clinical Biostatistics} % Event
  {Newcastle, UK} % Location
  {Aug. 2022} % Date(s)

%---------------------------------------------------------

\cvhonor
  {Open Science Summer School}
  [@EPFL, organized by EPFL and ETH PhD students]
  {Lausanne, Switzerland}
  {Jun. 2022}


%---------------------------------------------------------
\cvhonor
  {International workshop on cancer prevention} % Event
  [Understanding hormone signaling and its risk on estrogen receptor-positive breast cancer] % Talk
  {Pollone, Italy} % Location
  {Jun. 2022} % Date

%---------------------------------------------------------
\cvhonor
  {Basel Computational Biology Conference - BC2} % Event
  [Estrogen signature and gene coexpression network for breast cancer stratification and survival analysis] % Poster or talk
  {Basel, Switzerland} % Location
  {Sep. 2021} % Date(s)


%---------------------------------------------------------
\cvhonor
  {XII Regional Topology Meeting} % Event
  [A topological approach to protein stability] % Poster or talk
  {Águas de Lindóia, Brazil} % Location
  {Oct. 2019} % Date(s)


%---------------------------------------------------------
\cvhonor
  {Geometric Data Analysis} % Event
  [Persistent homology and the protein folding problem] % Poster or talk
  {Chicago, USA} % Location
  {May 2019} % Date(s)

%---------------------------------------------------------
\cvhonor
  {Data Driven Dynamics: Algebraic Topology, Combinatorics and Analysis} % Event
  [Persistent homology and the protein folding problem] % Poster or talk
  {Montreal, Canada} % Location
  {Apr. 2019} % Date(s)

%---------------------------------------------------------
\cvhonor
  {8th Workshop of Thesis and Dissertations of ICMC} % Event
  [Optimal cycles and applications in machine learning] % Poster or talk
  {São Carlos, Brazil} % Location
  {Aug. 2018} % Date(s)

%---------------------------------------------------------
\cvhonor
  {XXI Brazilian Topology Meeting} % Event
  [Optimal cycles and applications in machine learning] % Poster or talk
  {Niteroi, Brazil} % Location
  {Aug. 2018} % Date(s)

%---------------------------------------------------------
\cvhonor
  {TRIPODS Summer Bootcamp: Topology and machine learning} % Event
  [Optimal cycles and applications in machine learning] % Poster or talk
  {Providence, USA} % Location
  {Aug. 2018} % Date(s)

%---------------------------------------------------------
\cvhonor
  {Automatic sequences, Number Theory, Aperiodic Order} % Event
  % % Poster or talk
  {Delft, The Netherlands} % Location
  {Oct. 2015} % Date(s)

%---------------------------------------------------------
\cvhonor
  {Panorama of Mathematics} % Event
  % % Poster or talk
  {Bonn, Germany} % Location
  {Oct. 2015} % Date(s)

%---------------------------------------------------------
\end{cvhonors}
