%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Teaching and Outreach}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  \cventry
    {PhD Student/Lab immersion supervisor} % Affiliation/role
    {EPFL} % Organization/group
    {Lausanne, Switzerland} % Location
    {Sep. 2022 - Dec. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
          \item Proposed and supervised a lab immersion project for a 
                master's student. The student worked weekly on the lab in a 
                project involving the tool TTMap.
      \end{cvitems}
    }
 
 \cventry
    {PhD Student/Teaching Assistant} % Affiliation/role
    {EPFL} % Organization/group
    {Lausanne, Switzerland} % Location
    {Sep. 2020 - current} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
          \item Teaching assistant of genomics and bioinformatics for over 100 
                students in 2022 and 2023. Organized exercise sessions and 
                students projects for the final assignments. Supervised more
                10 students in the final project where they had to reproduce
                figures from several papers.
          \item Started and organize bi-weekly seminars with experts on cancer
                prevention. The main audience is a group of european 
                researchers and PhD students working under the same Marie Curie
                grant, a highly prestigious grant awarded by EU.  
          \item Started and organized a monthly bioinformatics journal club for
                newly started PhD students from the network above.
          \item Helped students with exercises and concepts in 
                Numerical Analysis, a course with over 150 students.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Core Member, funded by national government} % Affiliation/role
    {PET - Educational Project} % Organization/group
    {Curitiba, Brazil} % Location
    {Aug. 2013 - Jul. 2014, Mar. - Jun. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Developed teaching resources to teach high leve mathematics
        to 100 high school students during one week. The topics were:
        \begin{itemize}
          \item Number Theory and Criptograhy;
          \item Euclidean and Non-Euclidean geometries.
        \end{itemize}}
        \item {Organized an one week long academic session for math students,
        with courses and invited lectures.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Federal University of Paraná} % Organization/group
    {Teaching Assistant - Analytic Geometry} % Affiliation/role
    {Curitiba, Brazil} % Location
    {Mar. 2016 - Jun. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Organized weekly meetings with students to help them and solve
        problems in Analytic Geometry.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
